---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

httptest2::start_vignette("../man/figures/README")
```

# open311

<!-- badges: start -->
[![R-CMD-check](https://github.com/JsLth/open311/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JsLth/open311/actions/workflows/R-CMD-check.yaml)
[![](https://www.r-pkg.org/badges/version/rors)](https://cran.r-project.org/package=rors)
[![Codecov test coverage](https://codecov.io/gh/JsLth/open311/branch/main/graph/badge.svg)](https://app.codecov.io/gh/JsLth/open311?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/jslth/open311/badge/master)](https://www.codefactor.io/repository/github/jslth/open311/overview/master)
<!-- badges: end -->

`r311` is an R interface to the international standard [open311](https://www.open311.org/). open311 APIs are used for civic issue management and public service communication. The standard allows administrations to better manage citizen requests, citizens to more easily submit requests, and (hence this package) researchers and data scientists to access data regarding public service communication. `r311` supports the seamless management and add supplementation of available endpoints, the selection of appropriate APIs to access, and the retrieval of civic service and request data. Custom queries and extensions (e.g. from CitySDK) are implicitly supported. `r311` is designed to require a minimal amount of dependencies, but allow for easy integration into common R frameworks such as the tidyverse, `sf` or `xml2`.

## Installation

You can install the development version of open311 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JsLth/open311")
```

## Example

The following example loads `open311`, sets up a jurisdiction and retrieves
a small amount of data on service tickets in Cologne, Germany.

```{r example}
library(open311)

o311_api("Cologne")
o311_requests()
```

