---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

httptest2::start_vignette("../man/figures/README")
```

# open311

<!-- badges: start -->
[![R-CMD-check](https://github.com/JsLth/open311/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JsLth/open311/actions/workflows/R-CMD-check.yaml)
[![](https://www.r-pkg.org/badges/version/rors)](https://cran.r-project.org/package=rors)
[![Codecov test coverage](https://codecov.io/gh/JsLth/open311/branch/main/graph/badge.svg)](https://app.codecov.io/gh/JsLth/open311?branch=main)
[![CodeFactor](https://www.codefactor.io/repository/github/jslth/open311/badge/master)](https://www.codefactor.io/repository/github/jslth/open311/overview/master)
<!-- badges: end -->

`open311` is an R package that allows you to query any endpoint that uses
the open311 API standard for public service communication. Usually, such APIs
are established alongside web services that allow citizens to submit public
service tickets on public spaces. These tickets can be retrieved using open311
APIs.

`open311` supports all official endpoints which currently include `services`
and `requests`.

## Installation

You can install the development version of open311 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JsLth/open311")
```

## Example

The following example loads `open311`, sets up a jurisdiction and retrieves
a small amount of data on service tickets in Cologne, Germany.

```{r example}
library(open311)

o311_jurisdiction("Cologne")
o311_requests()
```

